Concurrent Programming with Harmony

### 2020-08-03 book/paper.tex
Latest

  description={is a process that cannot change the state unless another

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/Up1.png}
\caption{The
\harmonyref{Up.html}{HTML output of running Harmony on \autoref{fig:inc}}.
There are three sections.
The top shows the steps to the problematic state.
The bottom left shows the source code and bytecode
of the program.
The bottom right shows the state of each process after the selected step.
Each row in the stack trace of a process shows the current program counter,
the method that is being evaluated, and the line of code that is
being evaluated.}
\label{fig:inchtml1}
\end{figure}

@@

We call a process \emph{blocked}
\index{blocked process}%
if the process can only change the state if another process changes
the state first.
A process trying to
acquire a test-and-set spinlock held by another process is a good example
of a process being blocked.
The only way forward is if the other process releases the lock.

>>>>

  description={is a process that cannot change the state or terminate unless another

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/Up1-crop.pdf}
\caption{The
\harmonyref{Up.html}{HTML output of running Harmony on \autoref{fig:inc}}.
There are three sections.
The top shows the steps to the problematic state.
The bottom left shows the source code and bytecode
of the program.
The bottom right shows the state of each process after the selected step.
Each row in the stack trace of a process shows the current program counter,
the method that is being evaluated, and the line of code that is
being evaluated.}
\label{fig:inchtml1}
\end{figure}

@@

We call a process \emph{blocked}
\index{blocked process}%
if the process can only change the state or terminate if another process
changes the state first.
A process trying to
acquire a test-and-set spinlock held by another process is a good example
of a process being blocked.
The only way forward is if the other process releases the lock.
